\documentclass[margin,line,10pt]{res}
\usepackage{textgreek}
\usepackage{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Dr. Firstname Lastname, PhD \vspace*{.1in}}

\address{firstname.lastname@gmail.com, \url{https://www.akdiem.com}, \url{https://github.com/akdiem}}

\begin{resume}

  {\sc Research Interests} List a few comma separated keywords \\

Short statement about your research interests. Try not to exceed 10 lines.\\

\vspace*{-.2in}

{\sc Current Position}\\
\vspace*{-.35in}
\section{\sc since mm/yyyy}{\bf Postdoctoral Fellow}, Department, Institution, City, Country\\
{\em Project:} project name, number, brief description\\

\vspace*{-.2in}

{\sc Previous Positions}\\
\vspace*{-.35in}
\section{\sc mm/yyyy--mm/yyyy}{\bf Postdoctoral Fellow}, Department, Institution, City, Country\\
Brief (specific) description of role.\\

\vspace*{-.2in}

{\sc Education}\\
\vspace*{-.35in}
\section{\sc yyyy}{\bf PhD}, Department, Institution, City, Country\\
Supervisors: Prof. Firstname Lastname, Dr. Firstname Lastname\\
\vspace*{-.35in}
\section{\sc yyyy}{\bf MSc Computer Science}, Department, Institution, City, Country\\
Supervisor: Dr. Firstname, Lastname\\

\vspace*{-.2in}

{\sc Research Mobility}\\
\vspace*{-.35in}
\section{\sc mm/yyyy--mm/yyyy}Department, Institution, City, Country\\
Brief (specific) description of purpose.

\vspace*{-.2in}

{\sc Fellowships, Awards and Prizes}\\
\vspace*{-.35in}
\section{\sc yyyy}{\bf Grant X}, Department, Institution, City, Country\\
\vspace*{-.35in}
\section{\sc yyyy}{\bf Prize Y}, Department, Institution, City, Country\\

\vspace*{-.2in}

{\sc Supervision}\\
\vspace*{-.35in}
\section{\sc yyyy}{\bf 1 MSc student}, Department, Institution, City, Country\\
Brief (specific) description of project and outcoms.\\
\vspace*{-.35in}
\section{\sc yyyy}{\bf 1 summer intern}, Department, Institution, City, Country\\
Brief (specific) description of project and outcome.\\

\vspace*{-.2in}

{\sc Teaching}\\
\vspace*{-.35in}
\section{\sc mm/yyyy--mm/yyyy}{\bf Demonstrator}, Department, Institution, City, Country\\
Brief (specific) description of class(es)\\

\vspace*{-.2in}

{\sc Organisation of Scientific Meetings}\\
\vspace*{-.35in}
\section{\sc mm/yyyy}{\bf Conference Chair}, Conference, City, Country\\

\vspace*{-.2in}

{\sc Publications}\\
h-index: 5, i10-index: 5\\
\vspace*{-.35in}
\section{\sc 2018}
{\bf Me}, Author2, Author3 (yyyy) Title. \textit{Journal} Vol (Issue): pages, \url{https://doi.org}\\
{\bf Me}, Author2, Author3 (yyyy) Title. \textit{Journal} Vol (Issue): pages, \url{https://doi.org}\\      
\vspace*{-.35in}
\section{\sc 2017}
Author1, {\bf Me} (yyyy) Title. \textit{Journal} Vol (Issue): pages, \url{https://doi.org}\\

\vspace*{-.2in}

{\sc Conference Contributions}\\
\vspace*{-.35in}
\section{\sc 2018}
Title. \textit{Conference name}, Dates, City, Country\\
Title. {\bf (invited)} \textit{Conference name}, Dates, City, Country\\   
\vspace*{-.35in}
\section{\sc 2017}
Title. \textit{Conference name}, Dates, City, Country\\

\vspace*{-.2in}

{\sc Reviewer}\\
\vspace*{-.35in}
Journal name\\
Journal name\\
Journal name\\

\end{resume}
\end{document}
